\hyperlink{classVtxExtendedVertexFinder}{Vtx\-Extended\-Vertex\-Finder}

\subsection*{Data}

Runs the extended vertex finder using Reco\-Digits in the store.

The extended vertex finder uses the \hyperlink{classMinuitOptimizer}{Minuit\-Optimizer} and \hyperlink{classVertexGeometry}{Vertex\-Geometry} classes in the \hyperlink{classDataModel}{Data\-Model} to reconstruct the muon vertex and direction. Minuit searches for the vertex position, time, and direction that minimizes the negative log likelihood function formed using extended hit residuals. For any given \hyperlink{classRecoDigit}{Reco\-Digit}, the extended hit residual is evaluated by assuming a muon travels along the vertex direction at the speed of light, and that a photon left the track at the Cherenkov angle to hit the Digit.

\subsection*{Configuration}

Describe any configuration variables for \hyperlink{classVtxExtendedVertexFinder}{Vtx\-Extended\-Vertex\-Finder}.

``` verbosity int Controls the level of information printed out while running Tool\-Analysis.

Use\-True\-Vertex\-As\-Seed bool If Using Monte Carlo data, the true muon position and direction are given to Minuit as the seed for the extended vertex finder.

Fit\-All\-On\-Grid\-Seed bool If 1, the Extended Vertex Fitter is executed using every position on the seed grid generated with the Vtx\-Seed\-Finder tool. For each position, a direction seed is generated using the \char`\"{}\-Find\-Simple\-Direction\char`\"{} tool. The fit that has the highest F\-O\-M and converges in Minuit is accepted as the reconstructed vertex.

If the above two bools are false, the Extended Vertex Finder is executed assuming that the usual full reconstruction chain has been executed. Specifically, the Extended Vertex Finder is ran using the Point\-Vertex\-Finder's result as the seed.

``` 